%----------------------------------------------------------------------------------------
%	DOCUMENT CONFIGURATION
%----------------------------------------------------------------------------------------
\documentclass[10pt,a4paper]{article}	
\usepackage[utf8]{inputenc}		
\usepackage[T1]{fontenc}
\usepackage[default]{raleway}
\usepackage[a4paper, margin=1.5cm, top=1.2cm, bottom=1.5cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage{multicol}

% Color Definitions
\definecolor{sectcol}{RGB}{0,100,200} % Professional Blue
\definecolor{textcol}{RGB}{50,50,50}
\definecolor{lightgray}{RGB}{120,120,120}

\hypersetup{
    colorlinks=true,
    urlcolor=sectcol,
    pdfauthor={Gabriel Matheus Oliveira},
    pdftitle={Resume - Gabriel Matheus Oliveira}
}

% Paragraph and Spacing Adjustments
\setlength{\parindent}{0mm}
\setlist[itemize]{nosep, leftmargin=1em, labelsep=0.5em} % Compact lists

%----------------------------------------------------------------------------------------
%	CUSTOM COMMANDS
%----------------------------------------------------------------------------------------

% Styled Section Header
\newcommand{\cvsection}[1]{
    \vspace{12pt}
    {\large\textcolor{sectcol}{\textbf{\MakeUppercase{#1}}}}
    \vspace{2pt}
    \hrule height 0.5pt \relax
    \vspace{6pt}
}

% Experience/Education Event
% Usage: \cvevent{date}{role}{company}{description}
\newcommand{\cvevent}[4]{
    \noindent \textbf{#2} \hfill \textcolor{sectcol}{\small \faCalendar* #1} \\
    \noindent \textit{\textcolor{lightgray}{#3}} \vspace{4pt} \\
    {#4} \vspace{8pt}
}

%----------------------------------------------------------------------------------------
%	DOCUMENT BEGINS
%----------------------------------------------------------------------------------------
\begin{document}

%--- HEADER ---
\begin{center}
    {\Huge \textbf{GABRIEL MATHEUS OLIVEIRA}} \\
    \vspace{6pt}
    {\color{sectcol} \large \faCode \ Systems Analyst | Industrial Automation Technician} \\
    \vspace{10pt}
    
    \small
    \faMapMarker* Uberaba -- MG, Brazil \quad 
    \faPhone* +55 (34) 99289-1596 \quad 
    \faEnvelope \ \href{mailto:gab_matheus@hotmail.com}{gab\_matheus@hotmail.com} \\
    \vspace{4pt}
    \faLinkedin \ \href{https://linkedin.com/in/oliveiragm}{linkedin.com/in/oliveiragm} \quad 
    \faGithub \ \href{https://github.com/GabMatheus}{github.com/GabMatheus} \quad 
    \faGlobe \ \href{https://gabmatheus.github.io/Portfolio/}{https://gabmatheus.github.io/Portfolio}
\end{center}

%--- PROFESSIONAL SUMMARY ---
\cvsection{Professional Summary}
Systems Analyst with a strong technical and academic background. Multi-disciplinary experience integrating software and web development, business process automation, and industrial automation. Proven track record in designing and building Python-based scripts for routine automation, providing specialized ERP system support, and managing IT infrastructure. Additionally active in the industrial sector, specializing in automation and instrumentation by designing and modifying electrical blueprints in AutoCAD and programming PLC environments.

%--- PROFESSIONAL EXPERIENCE ---
\cvsection{Professional Experience}

\cvevent{03/2026 – Present}{Automation Technician}{KR Automação e Robótica}{
\begin{itemize}
    \item Analyzed control loops, programmed Siemens PLCs using the TIA Portal platform, and developed supervisory systems (WinCC/SCADA).
    \item Assembled, wired, and interconnected electrical panels for command and automation systems.
    \item Drafted technical drawings, electrical schematics, and comprehensive project documentation.
    \item Maintained and developed internal software applications to support operational workflows.
\end{itemize}
}

\cvevent{06/2021 – 10/2025}{Systems Analyst}{CONEFI LTDA}{
\begin{itemize}
    \item Developed Robotic Process Automation (RPA) tools and Python scripts to optimize internal workflows and eliminate manual tasks.
    \item Handled system integrations and relational database management (SQL) to guarantee consistency and corporate data flow.
    \item Provided specialized tier-2 and tier-3 technical support for enterprise ERP systems (EMSys3, AutoSystem, Domínio, Mastermaq), focusing on troubleshooting and parameterization.
    \item Managed, maintained, and expanded local network infrastructure and servers for the IT department.
    \item Prepared operational reports and provided technical assistance for strategic decision-making in system improvement projects.
    \item Managed technology assets, covering hardware specification, procurement, and vendor technical alignment.
\end{itemize}
}

\cvevent{2016 – 2019}{Industrial Instrument Mechanic II}{DBR Engenharia/Biano Engenharia}{
\begin{itemize}
    \item Performed maintenance, calibration, parameterization, and diagnostics on industrial instruments and sensors.   
    \item Installed and configured frequency inverters, three-phase electric motors, and electrical control panels.  
    \item Executed electro-mechanical assembly of automated systems and industrial structured cabling.  
    \item Read, interpreted, and executed complex electrical engineering blueprints and interconnection diagrams.
\end{itemize}
}

\cvevent{2014 – 2016}{Engineering / IT Intern}{TV Integração (Globo Network Affiliate)}{
\begin{itemize}
    \item Provided technical support for broadcasting systems and maintained local network infrastructure.
    \item Handled user support requests and monitored network operations.
\end{itemize}
}

%--- EDUCATION ---
\cvsection{Education}

\cvevent{Expected 06/2026}{B.S. in Analysis and Systems Development}{UFV / UNINTER}{
Curriculum focused on Software Engineering, Systems Analysis, Object-Oriented Programming (OOP), Software Architecture, IT Project Management, and Web Development.
}

\cvevent{Concluded}{Associate Degree in Electronics}{CEFET-MG}{
Technical program covering industrial automation, digital and analog circuits, embedded systems, and microcontrollers. Practical focus on PLC programming and electrical control design.
}

%--- TECHNICAL SKILLS ---
\cvsection{Technical Skills}

\begin{multicols}{2}
    \textbf{\faIndustry \ Automation \& Systems}
    \begin{itemize}
        \item PLC Programming (Siemens TIA Portal)
        \item Electrical Drafting (AutoCAD)
        \item Embedded Systems \& Microcontrollers
        \item Industrial Instrumentation \& Sensors
        \item Communication Networks \& Industrial Protocols
    \end{itemize}

    \columnbreak

    \textbf{\faLaptopCode \ Development \& IT}
    \begin{itemize}
        \item Databases (PostgreSQL, MySQL, SQL Server)
        \item Languages: HTML, CSS, JavaScript, Python, C, C++
        \item Version Control (Git) \& Linux Environments
        \item Advanced Technical Support \& ERP Administration
        \item Software Engineering \& SOLID Principles
    \end{itemize}
\end{multicols}

%--- COURSES AND CERTIFICATIONS ---
\cvsection{Courses \& Certifications}
\cvevent{2019}{General English (B2 Upper-Intermediate)}{OSCARS International -- Dublin/Ireland}{
6-month international exchange program focusing on communicative fluency and professional proficiency in global environments.
}

%--- PUBLICATIONS ---
\cvsection{Publications}
\cvevent{2021}{Technical Papers in Information Systems}{Academic Production}{
\begin{itemize}
    \item Authored research focusing on software quality models, component-based architecture, and GPU architecture/applications.
    \item \faGithub \ \href{https://github.com/GabMatheus/Pesquisas_Latex}{Repository featuring the LaTeX papers}
\end{itemize}
}

%--- PROFESSIONAL REFERENCES ---
\cvsection{Professional References}
\begin{itemize}[label=\faUserCheck, leftmargin=1.5em]
    \item \textbf{Bruno Lopes} | Operations Manager, Postos Alpa | (34) 98802-3389
    \item \textbf{Thiago Matias} | IT Coordinator, Conefi | (34) 98848-9918
    \item \textbf{Diego Militão} | Supervisor, DBR Engenharia | (34) 99184-9385
\end{itemize}

\vfill
\center{\footnotesize \textcolor{lightgray}{Document generated in \LaTeX \ | Available for validation via GitHub.}}

\end{document}
